\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
sections for MAB and problem def

\section{Preliminaries and Problem Statement}

In this section we describe the multi-arm bandit problem and the formal definition of our problem.

\subsection{Multi-Arm Bandit Problem}
The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.

@@

@@

\subsection{Multi-Arm Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
We have a policy for exploration of different grasp plans (i.e. choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.  
The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.

>>>>

\section{Multi-Arm Bandit Problem}
The multi-arm bandit problem originally described by Robbins \cite{robbins1985some} is a statistical decision model of an agent trying to make correct decisions, while gathering information at the same time.
The traditional setting of a multi-arm bandit problem is a gambler that has K independent slot machine arms and tries to infer which one will yield the highest reward.
A successful gambler would want to exploit the machine that currently yields the highest reward and explore new arms to see if they give better rewards.
Developing a policy that successfully trades between exploration and exploitation has been the focus of extensive research, since the problem formulation \cite{bubeck2009pure}, \cite{robbins1985some}, \cite{bergemann2006bandit}.

@@

\section{Problem Definition}
Before we present the problem definition, we introduce the grasping model, the line of action.

@@

\section{Multi-Arm Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to simply perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-arm bandit problem and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
We have a policy for exploration of different grasp plans (i.e. choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.  
The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.
